How to compute the fusion product of MV cycles in type A

### 2021-05-16 draft.tex
hit sect 7

\acom{I started changing $\OO$ to $\CC[t]$ but we should rather change it to $R$ as we'll want this notation for $R = \CC[t]$ as well as $\cO$?}

@@

On the other hand, by definition 
$$
Z(\tau)_2 \subset \{ L \in S^\mu : L \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
$$
\acom{Need $L_{\{1,..,i\}}$}
\jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
\subsection{Fusion of MVCs via BD MVy}
Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
% 
Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. \acom{We could also use a more compact notation like $A_{(p)}$}
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}

Given $s\in\CC\setminus \{0\}$, and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
% 
\begin{equation*}
    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
\end{equation*}
% 
and
% 
\begin{equation*}
    X(\tau')\ast_{\CC^\times} X(\tau'') = 
    \left\{
        (A,s)\in M_N(\CC) \times \CC^\times: 
        A \in X(\tau') \ast_s X(\tau'') 
    \right\}\,.
\end{equation*}
% 
% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}

@@

\begin{proposition}
    % Given $b_{Z'},b_{Z''}\in\CC[N]$, 
    % Let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ 
    % be such that $t^{\lambda'}Z' = X(\tau')$ and $t^{\lambda''}Z'' = X(\tau'')$. 
    % and set $\mu = \mu' + \mu''$. If $s\ne 0$, then 
    The image of $X(\tau')\ast_s X(\tau'')$ under the isomorphism of \Cref{th:OTGrW} is dense in $Z(\tau')\ast_s Z(\tau'')$. 
    % \[
    % \overline{\phi(X(\tau',\tau''))} 
    % = Z'\ast_s Z'' \,. 
    % \]
\end{proposition}
% 
% \jcom{Do you want the ``blocky'' or ``boxy'' description here?  I mean, do you want $ i = 1, \dots, N$ or $ i =1, \dots, m$? I'm not so sure that ``boxy'' will work, since with those $s$ in the matrix, it doesn't preserves all the $ \CC^i$.}

@@

\begin{proof}
    % We wish to apply \Cref{prop:dth}. Nope
    % We will also need \Cref{le:Grl1l2}. Nope 
    % Consider the following diagram.
    % \[
    % \begin{tikzcd}
    %     X'\ast_s X'' \ar[r,dashed,"?"] \ar[d,"\bar g"] & X'\times X'' \ar[d," \phi\times \phi"] \\ 
    %     \Gr_{0,s}\ar[r,"\tau_s"] & \Gr\times\Gr
    % \end{tikzcd}
    % \]
    % \acom{Not sure what's a good notation for the vertical arrows. Don't want to introduce $\phi$. $\bar g(A) = g(A)\CC[t]^m$ temporarily.}
    % We show that the image of $\tau_s\circ \bar g$ coincides with the image of $\phi\times\phi$ which is dense in $Z'\times Z''$ by \Cref{prop:dth}.
    % % 
    Let $A\in X(\tau')\ast_s X(\tau'')$ and $i = 1,\dots, m$.  
    % Denote by 
    % $E_a$ the generalized $a$-eigenspace of $A$, and by 
    The lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
    $$
    L\cap \CC[t]^i = l
    $$
    where $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denotes the $\CC[t]$-submodule generated by the first $i$ standard basis vectors.
    %

@@

So $A\in\dots$ iff $g(A)\in\dots$ 
\end{proof}
% 
% 
In analogy with the Beilinson--Drinfeld construction \acom{add loc cit} we define $X(\tau')\ast_0 X(\tau'')$ to be the zero fibre of the family $\overline{\bigcup_{s\in\CC\setminus\{0\}} X(\tau')\ast_s X(\tau'')}$ in $M_N(\CC)$. 
% 
\begin{corollary}
    $X'\ast_0 X'' \cong Z'\ast_0 Z''$ 
\end{corollary}
% 
Let $X(\tau)$ be the top-dimensional \acom{speak to this?} irreducible component of
% from $\tau\in YT(\lambda)_\mu$ by 
\[
% X(\tau) = 
% \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}\,. 
% }    
\]
Then $\overline{X(\tau)}$ is called a \textbf{generalized orbital variety}. 
%

\begin{theorem}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{\overline{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{theorem}
\acom{$\overline{X(\tau)}$ vs $Z(\tau) = \overline{al;sdj}$}
\begin{corollary}
    $X'\ast_0 X''$ is a union of GOVs.
\end{corollary}
\begin{proof}
    Since $X'\ast_0 X''\subset \overline{\OO}^\lambda\cap\TT_\mu\cap\n$\dots 
\end{proof}

>>>>

\acom{I started changing $\OO$ to $\CC[t]$ but we should rather change it to $R$ as we'll want this notation for $R = \CC[t]$ as well as $\cO$? Also, don't we want $L_\gamma = R^m/L^{\gamma^c}$}

@@

On the other hand, by definition 
$$
Z(\tau)_2 \subset \{ L \in S^\mu : L \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
$$
\acom{Need $L_{\{1,..,i\}}$ here.}

\jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
\subsection{Fusion of MVCs via BD MVy}
Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
% 
\begin{theorem}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{theorem}
% 
Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. \acom{We could also use a more compact notation like $A_{(p)}$}
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}

Given $s\in\CC^\times$ and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
% 
\begin{equation*}
    \mathring X(\tau',\tau'')_{0,s} 
    % X(\tau')\ast_s \mathring X(\tau'') 
    = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}
\end{equation*}
% 
and
% 
\begin{equation*}
    % X(\tau')\ast_{\CC^\times} X(\tau'') = 
    \mathring X(\tau',\tau'')_{0,\CC^\times} = 
    \left\{
        (A,s)\in M_N(\CC) \times \CC^\times: 
        A \in X(\tau') \ast_s X(\tau'') 
    \right\}\,.
\end{equation*}
% 
% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}

@@

\begin{proposition}
    % Given $b_{Z'},b_{Z''}\in\CC[N]$, 
    % Let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ 
    % be such that $t^{\lambda'}Z' = X(\tau')$ and $t^{\lambda''}Z'' = X(\tau'')$. 
    % and set $\mu = \mu' + \mu''$. If $s\ne 0$, then 
    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is dense in $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$. 
    % \[
    % \overline{\phi(X(\tau',\tau''))} 
    % = Z'\ast_s Z'' \,. 
    % \]
\end{proposition}
% 
% \jcom{Do you want the ``blocky'' or ``boxy'' description here?  I mean, do you want $ i = 1, \dots, N$ or $ i =1, \dots, m$? I'm not so sure that ``boxy'' will work, since with those $s$ in the matrix, it doesn't preserves all the $ \CC^i$.}

@@

\begin{proof}
    % We wish to apply \Cref{prop:dth}. Nope
    % We will also need \Cref{le:Grl1l2}. Nope 
    % Consider the following diagram.
    % \[
    % \begin{tikzcd}
    %     X'\ast_s X'' \ar[r,dashed,"?"] \ar[d,"\bar g"] & X'\times X'' \ar[d," \phi\times \phi"] \\ 
    %     \Gr_{0,s}\ar[r,"\tau_s"] & \Gr\times\Gr
    % \end{tikzcd}
    % \]
    % \acom{Not sure what's a good notation for the vertical arrows. Don't want to introduce $\phi$. $\bar g(A) = g(A)\CC[t]^m$ temporarily.}
    % We show that the image of $\tau_s\circ \bar g$ coincides with the image of $\phi\times\phi$ which is dense in $Z'\times Z''$ by \Cref{prop:dth}.
    % % 
    Let $A\in X(\tau')\ast_s X(\tau'')$ and $i = 1,\dots, m$.  
    % Denote by 
    % $E_a$ the generalized $a$-eigenspace of $A$, and by 
    The lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
    $$
    % L\cap \CC[t]^i = l
    l\cong L_{1,..,i}
    $$
    where $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denotes the $\CC[t]$-submodule generated by the first $i$ standard basis vectors.
    %

@@

So $A\in\dots$ iff $g(A)\in\dots$ 
\end{proof}
% 
% 
In analogy with the Beilinson--Drinfeld construction \acom{add loc cit} we define $X(\tau')\ast_0 X(\tau'')$ to be the zero fibre of the family $\overline{\bigcup_{s\in\CC\setminus\{0\}} X(\tau')\ast_s X(\tau'')}$ in $M_N(\CC)$. 
% 
\begin{corollary}
    The image of $X'\ast_0 X''$ in $\cong Z'\ast_0 Z''$ is dense and $\iota(X(\tau),X(\tau',\tau'')) = \iota(Z(\tau),Z(\tau')\circ Z(\tau''))$. 
\end{corollary}
% 
Let $X(\tau)$ be the top-dimensional \acom{speak to this?} irreducible component of
% from $\tau\in YT(\lambda)_\mu$ by 
\[
% X(\tau) = 
% \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}\,. 
% }    
\]
Then $\overline{X(\tau)}$ is called a \textbf{generalized orbital variety}. 
%

\begin{corollary}
    $X'\ast_0 X''$ is a union of GOVs.
\end{corollary}
\begin{proof}
    Since $X'\ast_0 X''\subset \overline{\OO}^\lambda\cap\TT_\mu\cap\n$\dots 
\end{proof}
